---
title: "admin"
format: html
params:
  pull_databraryr: false
  verbose_login: true
  switch_account: false
---

## About

This page tests administrative functions using an account on the staging server.
It makes use of credentials specific to that account.
The credentials are stored in `~/.Renviron`.

## Setup

```{r}
#| label: pull-new-databraryr
if (params$pull_databraryr) {
  message("Pulling latest version of `databraryr` from GitHub.")
  remotes::install_github(repo = "NYU-Databrary/databraryr", ref = "development")
} else {
  message("Using installed version of `databraryr`.")
}

```

To switch between accounts, open '~/.Renviron`, uncomment the relevant environment variables

```{r}
#| label: "edit-renviron"
#| eval: false

if (params$switch_account) {
  source("R/restart_r.R")
  usethis::edit_r_environ(scope = "user")
}
```

Then restart R.

Now, we can confirm that the correct API endpoint and user account are selected.

```{r}
library(databraryr)
databraryr:::DATABRARY_BASE_URL
Sys.getenv("DATABRARY_LOGIN")
```

## Login

```{r}
#| label: "login to Databrary (staging)"

login_db(email = Sys.getenv("DATABRARY_LOGIN"),
         password = Sys.getenv("DATABRARY_PASSWORD"),
         client_id = Sys.getenv("DATABRARY_CLIENT_ID"),
         client_secret = Sys.getenv("DATABRARY_CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE)
```

### Check `whoami()`

```{r}
who <- whoami()

message(who$message, "\nGreat news, user: ", who$user)
```

## Test `get_*` functions

These functions retrieve usage statistics.

### Check `get_institution_statistics()`

```{r}
databraryr::get_institution_statistics(institution_id = 8) # NYU 
```

### Check `get_user_statistics()`

```{r}
databraryr::get_user_statistics(user_id = 5) # Karen Adolph
```

## Clean-up

```{r}
logout_db()
```
