---
title: "Records and Measures"
format: html
params:
  test_vol_id: 1777
  test_endpoint: "production" # {production,staging}
  prod_api: "https://api.databrary.org"
  staging_api: "https://api.stg-databrary.its.nyu.edu"
---

## About

This page documents testing of the functions that relate to records and measures.

::: callout-important
Most of the examples below were created by Pawel Armatys from Montrose Software.
:::

## Setup

```{r}
#| label: check-endpoint
#| 
assertthat::is.string(params$test_endpoint)
assertthat::is.string(params$prod_api)
assertthat::is.string(params$staging_api)

this_endpoint <- databraryr:::DATABRARY_BASE_URL

if (params$test_endpoint == "production") {
  message("Test target: Production API.")
  if (this_endpoint == params$prod_api) {
    message("Databraryr API target endpoint is correct.")
  } else {
    message(paste0(
      "Target: ",
      params$test_endpoint,
      " | databraryr base: ",
      this_endpoint
    ))
    stop(
      "`databraryr` API target endpoint does not match testing target endpoint. Check ~/.Renviron."
    )
  }
} else if (params$test_endpoint == "staging") {
  message("Test target: Staging API.")
  if (this_endpoint == params$staging_api) {
    message("Databraryr API target endpoint is correct.")
  } else {
    message(paste0(
      "Target: ",
      params$test_endpoint,
      " | databraryr base: ",
      this_endpoint
    ))
    stop(
      "`databraryr` API target endpoint does not match testing target endpoint. Check ~/.Renviron."
    )
  }
} else {
  stop("API endpoint not specified properly")
}
```

```{r}
#| label: "login to Databrary"
library(databraryr)

login_db(email = Sys.getenv("DATABRARY_LOGIN"),
         password = Sys.getenv("DATABRARY_PASSWORD"),
         client_id = Sys.getenv("DATABRARY_CLIENT_ID"),
         client_secret = Sys.getenv("DATABRARY_CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE,
         vb = TRUE)
```
## List categories and metrics

```{r}
#| label: list-categories 
cats <- list_categories()
cats
```

### Participant

Show category 1 (participant) metrics.

```{r}
participant_metrics <- cats$metrics[[which(cats$category_id == 1)]]
purrr::map_dfr(participant_metrics, ~ tibble::tibble(
  metric_id   = .x$metric_id,
  metric_name = .x$metric_name,
  metric_type = .x$metric_type,
  required    = .x$metric_required
))

```

Show category definition.

```{r}
get_category_by_id(category_id = 1)
```

### Pilot metrics

```{r}
pilot_metrics <- cats$metrics[[which(cats$category_id == 2)]]
purrr::map_dfr(pilot_metrics, ~ tibble::tibble(
  metric_id   = .x$metric_id,
  metric_name = .x$metric_name,
  metric_type = .x$metric_type,
  required    = .x$metric_required
))

```

Show category definition.

```{r}
get_category_by_id(category_id = 2)
```

### Exclusion metrics

```{r}
exclusion_metrics <- cats$metrics[[which(cats$category_id == 3)]]
purrr::map_dfr(exclusion_metrics, ~ tibble::tibble(
  metric_id   = .x$metric_id,
  metric_name = .x$metric_name,
  metric_type = .x$metric_type,
  required    = .x$metric_required
))

```

Show category definition.

```{r}
get_category_by_id(category_id = 3)
```

### Condition metrics

```{r}
condition_metrics <- cats$metrics[[which(cats$category_id == 4)]]
purrr::map_dfr(condition_metrics, ~ tibble::tibble(
  metric_id   = .x$metric_id,
  metric_name = .x$metric_name,
  metric_type = .x$metric_type,
  required    = .x$metric_required
))

```

Show category definition.

```{r}
get_category_by_id(category_id = 4)
```

### Group metrics

```{r}
group_metrics <- cats$metrics[[which(cats$category_id == 5)]]
purrr::map_dfr(group_metrics, ~ tibble::tibble(
  metric_id   = .x$metric_id,
  metric_name = .x$metric_name,
  metric_type = .x$metric_type,
  required    = .x$metric_required
))

```

Show category definition.

```{r}
get_category_by_id(category_id = 5)
```

### Task metrics

```{r}
task_metrics <- cats$metrics[[which(cats$category_id == 6)]]
purrr::map_dfr(task_metrics, ~ tibble::tibble(
  metric_id   = .x$metric_id,
  metric_name = .x$metric_name,
  metric_type = .x$metric_type,
  required    = .x$metric_required
))

```

Show category definition.

```{r}
get_category_by_id(category_id = 6)
```

### Context metrics

```{r}
context_metrics <- cats$metrics[[which(cats$category_id == 7)]]
purrr::map_dfr(task_metrics, ~ tibble::tibble(
  metric_id   = .x$metric_id,
  metric_name = .x$metric_name,
  metric_type = .x$metric_type,
  required    = .x$metric_required
))

```

Show category definition.

```{r}
get_category_by_id(category_id = 7)
```

## Show/edit categories enabled

```{r}
#| label: get-volume-enabled-categories
#| 
enabled <- get_volume_enabled_categories(vol_id = params$test_vol_id)
purrr::map_chr(enabled, "name")
```

Enable a category that is not currently enabled.

```{r}
#| label: enable-volume-category

enabled_ids <- purrr::map_int(enabled, "id")
not_enabled <- !((1:7) %in% enabled_ids)
if (sum(not_enabled) > 0) {
  new_category <- sample((1:7)[not_enabled], 1)
  new_category
}

# Enable a single additional category
enable_volume_category(vol_id = params$test_vol_id, category_id = new_category)
before_categories <- get_volume_enabled_categories(vol_id = params$test_vol_id) |>
  purrr::map_chr("name")

before_categories
```

Replace enabled categories.

```{r}
#| label: set-volume-enabled-categories
#| 
# Or replace the full enabled set in one call
set_volume_enabled_categories(vol_id = params$test_vol_id, category_ids = c(1L, 6L, 7L))
after_categories <- get_volume_enabled_categories(vol_id = params$test_vol_id) |>
  purrr::map_chr("name")

after_categories
```

## Create record

```{r}
#| label: create-volume-record

p_name <- date() |> stringr::str_replace_all(pattern = "[ ]+", "-")
p001 <- create_volume_record(
  vol_id      = params$test_vol_id,
  category_id = 1L,
  # participant
  name        = p_name, # stored as metric 1 "ID"
  measures    = list(
    "5" = "Female", # metric 5: gender
    "4" = list(year = 2000, month = 6, day = 15)  # metric 4: birthdate
  )
)

p001
```

```{r}
#| label: create-random-string-for-task-name
name_str <- sample(letters, 5) |> 
  paste(collapse="")
task <- create_volume_record(
  vol_id      = params$test_vol_id,
  category_id = 6L,           # task
  name        = name_str
)
task$record_id
```

Modify the task record by adding a description field.

```{r}
#| label: add-description-to-task-record
# Add a description to the task record
set_record_measure(
  vol_id    = params$test_vol_id,
  record_id = p001$record_id,  
  metric_id = 30L,               # description
  value     = paste0("Participants searched for ", name_str, " among distractors.")
)

```

Modify the prior gender value.

```{r}
#| label: set-record-measure
# Update gender on the participant record
set_record_measure(
  vol_id    = params$test_vol_id,
  record_id = p001$record_id,  
  metric_id = 5L,
  value     = "Male"           # overwrites previous "Female"
)

```

::: callout-note
`set_record_measure()` returns the raw measure object. `update_volume_record()` accepts a full measures list and returns the updated record in the same shape as create_volume_record(). Because it validates that all required metrics are present, it is safer to fetch current measures first and merge your change in.
:::

```{r}
#| label: change-gender-to-non-binary
current <- get_volume_record_by_id(vol_id = params$test_vol_id, record_id = p001$record_id)
new_measures <- utils::modifyList(current$measures, list("5" = "Non-binary"))
updated_p001 <- update_volume_record(
  vol_id    = params$test_vol_id,
  record_id = p001$record_id,
  measures  = new_measures
)
updated_p001$measures[["5"]]
```

## Link record to session as default

```{r}
#| label: create-session-w-default-records
session <- create_session(
  vol_id         = params$test_vol_id,
  name           = "Sub-P001 Wave 1",
  date           = list(year = "1975", month = "10", day = "31"),
  default_records = c(p001$record_id, task$record_id)
)
session$id
```

```{r}
#| label: add-default-record-to-session
add_default_record_to_session(
  vol_id     = params$test_vol_id,
  session_id = session$id,
  record_id  = p001$record_id 
)
```

```{r}
#| label: get-volume-record-by-id

this_volume_record <- get_volume_record_by_id(
  vol_id    = params$test_vol_id,
  record_id = p001$record_id
)

this_volume_record$default_sessions
```

Remove default from this session.

```{r}
#| label: remove-default-record-from-session
remove_default_record_from_session(
  vol_id     = params$test_vol_id,
  session_id = session$id,
  record_id  = task$record_id
)
```

## Assign records to a specific file

```{r}
#| label: list-volume-assets

vol_assets <- list_volume_assets(vol_id = params$test_vol_id)
sessions_w_assets <- vol_assets |>
  dplyr::select(session_id) |>
  unique()

pick_session_id <- sample(sessions_w_assets$session_id, 1)
assets <- list_session_assets(vol_id = params$test_vol_id, session_id = pick_session_id)
assets[, c("asset_id", "asset_name")]
```

Assign a task record to the 1st file.

```{r}
#| label: assign-record-to-file
assign_record_to_file(
  vol_id     = params$test_vol_id,
  session_id = pick_session_id,
  file_id    = assets$asset_id[1],
  record_id  = task$record_id  # 53139
)

```

## Edit records

::: {.callout-warning}
Editing records edits them globally.
:::

```{r}
#| label: edit-measure-30
set_record_measure(
  vol_id    = params$test_vol_id,
  record_id = task$record_id,  
  metric_id = 30L,
  value     = "UPDATED: Target was always a red circle. Revised 2024-10-01."
)
```

Now, confirm the change.

```{r}
#| label: get-updated-measure-info-from-volume
get_volume_record_by_id(
  vol_id    = params$test_vol_id,
  record_id = task$record_id
)$measures[["30"]]

```

## List volume records

All.

```{r}
#| label: list-all-volume-records
# All records
list_volume_records(vol_id = params$test_vol_id)
```

Participant only, showing the first record.

```{r}
#| label: list-volume-participant-records
this_vol_particip_records <- list_volume_records(vol_id = params$test_vol_id, 
                                                 category_id = 1L)

this_vol_particip_records$record_measures[1]
```

Delete (softly) a record from all sessions and files.

```{r}
#| label: soft-delete-record-from-sessions-files
p001

delete_volume_record(vol_id = params$test_vol_id, record_id = p001$record_id)

after_vol_particip_records <- list_volume_records(vol_id = params$test_vol_id, 
                                                 category_id = 1L)
```

Confirm deletion.

```{r}
#| label: confirm-record-deletion
p001$record_id %in% after_vol_particip_records$record_id
```

## Bulk operations

```{r}
#| label: create-10-participant-records-at-once

if (params$test_endpoint == "staging") {
  # Create ten participant records at once
  records_tbl <- bulk_create_records(
    vol_id       = params$test_vol_id,
    record_names = paste0("P", sprintf("%03d", 1:10)),
    category_id  = 1L
  )
  records_tbl
} else {
  message("Not on staging. Skipping test.")
}
```

Assign all of them as defaults to a (randomly chosen) session.

```{r}
#| label: bulk-assign-records-to-randomly-chosen-session

if (params$test_endpoint == "staging") {
  available_sessions <- list_volume_sessions(vol_id = params$test_vol_id)
  pick_session_id <- sample(available_sessions$session_id, 1)
  
  bulk_assign_records(
    vol_id     = params$test_vol_id,
    session_id = pick_session_id,
    record_ids = records_tbl$record_id
  )
} else {
  message("Not on staging. Skipping test.")
}
```

Remove all assignments from the previously chosen session.

```{r}
#| label: bulk-unassign

if (params$test_endpoint == "staging") {
  bulk_unassign_records(
    vol_id     = params$test_vol_id,
    session_id = pick_session_id,
    record_ids = records_tbl$record_id
  )
} else {
  message("Not on staging. Skipping test.")
}
```

Delete all records in volume.

::: {.callout-warning}
This is a highly destructive action.
Use with care.
:::

```r
# Delete all records
bulk_delete_records(vol_id = vol_id, record_ids = records_tbl$record_id)
```
