---
title: "Create/Update/Delete"
format: html
params:
  test_vol_id: 1777
  test_endpoint: "staging"
  prod_api: "https://api.databrary.org"
  staging_api: "https://api.stg-databrary.its.nyu.edu"
---

## About

This documents the results of testing functions that involve file uploads.

::: {.callout-important}
To make use of them, the tester must have write privileges on a Databrary volume.
:::

::: {.callout-warning}
These tests presume that the tester is accessing the test environment using a regular, Authorized Investigator, account.
:::

## Setup

```{r}
#| label: check-endpoint
#| 
assertthat::is.string(params$test_endpoint)
assertthat::is.string(params$prod_api)
assertthat::is.string(params$staging_api)

this_endpoint <- databraryr:::DATABRARY_BASE_URL

if (params$test_endpoint == "production") {
  message("Test target: Production API.")
  if (this_endpoint == params$prod_api) {
    message("Databraryr API target endpoint is correct.")
  } else {
    message(paste0(
      "Target: ",
      params$test_endpoint,
      " | databraryr base: ",
      this_endpoint
    ))
    stop(
      "`databraryr` API target endpoint does not match testing target endpoint. Check ~/.Renviron."
    )
  }
} else if (params$test_endpoint == "staging") {
  message("Test target: Staging API.")
  if (this_endpoint == params$staging_api) {
    message("Databraryr API target endpoint is correct.")
  } else {
    message(paste0(
      "Target: ",
      params$test_endpoint,
      " | databraryr base: ",
      this_endpoint
    ))
    stop(
      "`databraryr` API target endpoint does not match testing target endpoint. Check ~/.Renviron."
    )
  }
} else {
  stop("API endpoint not specified properly")
}
```

```{r}
#| label: "login to Databrary"
library(databraryr)

login_db(email = Sys.getenv("DATABRARY_LOGIN"),
         password = Sys.getenv("DATABRARY_PASSWORD"),
         client_id = Sys.getenv("DATABRARY_CLIENT_ID"),
         client_secret = Sys.getenv("DATABRARY_CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE,
         vb = TRUE)
```

## `create_*` functions

```{r}
#| label: create-folder
x <- assertthat::is.number(params$test_vol_id)
x <- assertthat::assert_that(params$test_vol_id > 0)

folder_name <- date() |> stringr::str_replace_all(pattern = " ", "-")
new_folder <- create_folder(vol_id = params$test_vol_id, name = folder_name)

new_folder
```

```{r}
#| label: create-session
session_name <- date() |> stringr::str_replace_all(pattern = " ", "-")
new_session <- create_session(vol_id = params$test_vol_id, name = session_name)

new_session
```

```{r}
#| label: create-volume-record
#| eval: false
#| 
record_P001 <- create_volume_record(
  vol_id = params$test_vol_id,
  category_id = 1,
  name = "P001",
  participant = list(birthday = list(
    year = 1776, month = 7, day = 04))
)

record_control_group <- create_volume_record(vol_id = params$test_vol_id,
                                             category_id = 6,
                                             name = "Control group")

record_task_A <- create_volume_record(
  vol_id = params$test_vol_id,
  category_id = 6,
  name = "Task A",
  measures = list("30" = "Extra value")
)

record_P001
record_control_group
record_task_A
```

::: {.callout-note}
2026-05-22: Gilmore needs more guidance about the standard procedure for associating records with sessions and files. So, I'm setting `eval: false` for the above chunk.
:::

## `upload_file`

```{r}
#| label: upload-png-file

png_path <- "files/upload_01/png_sample.png"

info_png <- upload_file(
  path =  png_path,
  destination_type = "session",
  object_id = new_session$id
)

info_png
```

```{r}
get_upload_status(info_png$status_url)
```

### `bulk_upload`

```{r}
#| label: bulk-upload-to-session-folder
# Upload to session
upload_01_files <- list.files("files/upload_01", full.names = TRUE)
upload_02_files <- list.files("files/upload_02", full.names = TRUE)

# Start the clock!
start_upload <- proc.time()
result_session <- bulk_upload_files(vol_id = params$test_vol_id, session_id = new_session$id,
                  file_paths = upload_01_files, preflight = TRUE)
proc.time() - start_upload

result_session
```

```{r}
#| label: bulk-upload-to-folder
# Upload to folder
start_upload <- proc.time()
result_folder <- bulk_upload_files(vol_id = params$test_vol_id, session_id = NULL,
                  file_paths = c(upload_01_files, upload_02_files),
                  folder_id = new_folder$id, preflight = TRUE)
proc.time() - start_upload

result_folder
```

## `bulk_rename_*` functions

In the code below, I set `n_to_rename` to 3, but confirm that there are at least 3 files or sessions before renaming.
If there aren't enough files or sessions, the chunk exits with an error message.

```{r}
#| label: bulk-rename-files
n_to_rename <- 3

these_files <- list_session_assets(session_id = new_session$id, vol_id = params$test_vol_id)

if(dim(these_files)[1] < n_to_rename) {
  n_to_rename = dim(these_files)[1]
}

if (n_to_rename < 1) {
  stop("No files to rename in volume ", params$test_vol_id, ", session ", new_session$id)
}

file_asset_ids <- these_files$asset_id[1:n_to_rename]
new_file_names <- stringr::str_replace(these_files$asset_name[1:n_to_rename], pattern = "_", replacement = "--")

bulk_rename_these <- bulk_rename_files(vol_id = params$test_vol_id,
                  session_id = new_session$id,
                  file_ids = file_asset_ids,
                  new_names = new_file_names)

renamed_files <- list_session_assets(session_id = new_session$id, vol_id = params$test_vol_id)

cbind(old_names = these_files$asset_name[1:n_to_rename], new_names = renamed_files$asset_name[1:n_to_rename])
```

```{r}
#| label: bulk-rename-sessions
#| eval: false
n_to_rename <- 3

these_sessions <- list_volume_sessions(vol_id = params$test_vol_id) |> 
  dplyr::arrange(desc(session_id))

if(dim(these_sessions)[1] < n_to_rename) {
  n_to_rename = dim(these_sessions)[1]
}

if (n_to_rename < 1) {
  stop("No sessions to rename in volume ", params$test_vol_id)
}

selected_session_ids <- these_sessions$session_id[1:n_to_rename]
new_session_names <- stringr::str_replace(these_sessions$session_name[1:n_to_rename], pattern = "-", replacement = "__")

bulk_rename_these <- bulk_rename_sessions(vol_id = params$test_vol_id, 
                                          session_ids = selected_session_ids,
                                          new_names = new_session_names)

renamed_sessions <- list_volume_sessions(vol_id = params$test_vol_id) |> 
  dplyr::arrange(desc(session_id))

cbind(old_names = these_sessions$session_name[1:n_to_rename], new_names = renamed_sessions$session_name[1:n_to_rename])
```

::: {.callout-warning}
2026-05-22: ROG to stop here. Why does the above code generate multiple session records with the same `session_name` and `session_id`?
I'm setting `eval: false` in the chunk above until we can squash this bug.
:::

## `delete_*` functions

```{r}
#| label: delete-folder
vol_folders <- list_volume_folders(vol_id = params$test_vol_id) |>
  dplyr::arrange(desc(folder_id))

delete_folder_id <- vol_folders$folder_id[1]

delete_folder(vol_id = params$test_vol_id, folder_id = delete_folder_id)
```

::: {.callout-note}
2026-05-22: ROG notes that none of the folders he created today show up under `list_volume_folders()`.
This doesn't block the above code from working, but it means that the procedure for deleting the "latest" folder isn't actually deleting the most recent folder.
Also, it looks like the create folder scheme is creating multiple folder copies with the same id's and names.
:::

```{r}
#| label: delete-session-file
vol_sessions <- list_volume_sessions(vol_id = params$test_vol_id) |>
  dplyr::arrange(desc(session_id))

delete_session_id <- vol_sessions$session_id[1]

session_files <- list_session_assets(session_id = delete_session_id, vol_id = params$test_vol_id)

session_files

if (dim(session_files)[1] > 0) {
  delete_asset_id <- vol_sessions$session_id[1]
  
  delete_session_file(
    vol_id = params$test_vol_id,
    session_id = delete_session_id,
    file_id = delete_asset_id
  )
  
  list_session_assets(session_id = delete_session_id, vol_id = params$test_vol_id)
} else {
  stop("No files to delete in volume ",
       params$test_vol_id,
       ", session ",
       delete_session_id)
}
```

::: {.callout-note}
2026-05-22: ROG notes that the file metadata does not show that the file has been deleted.
:::

```{r}
#| label: delete-session
vol_sessions <- list_volume_sessions(vol_id = params$test_vol_id) |>
  dplyr::arrange(desc(session_id))

# Before deletion
head(vol_sessions)

delete_session_id <- vol_sessions$session_id[1]

delete_session(vol_id = params$test_vol_id, session_id = delete_session_id)

# After deletion
list_volume_sessions(vol_id = params$test_vol_id) |>
  dplyr::arrange(desc(session_id)) |>
  head()
```

::: {.callout-warning}
2026-05-22: ROG unless otherwise noted, the chunks below have `eval: false` set to prevent them from running.
This leaves the document in a state that renders successfully while I add code to handle testing the remaining functions.
:::

```{r}
#| label: delete-functions
#| eval: false
delete_record_measure(vol_id = params$test_vol_id, record_id = record_control_group$record_id)

databraryr::delete_volume_record()
```

## `bulk_assign*` functions

```{r}
#| label: bulk-assign
#| eval: false
bulk_assign_records()
bulk_unassign_records()
```

### `bulk_{create,rename,delete}_*`

```{r}
#| label: bulk-create-name-delete
#| eval: false
bulk_create_folders()

bulk_create_records()

bulk_delete_files()

bulk_delete_folders()

bulk_delete_records()

bulk_delete_sessions()
```

### `check_duplicate_*` functions

```{r}
#| label: check-duplicates
#| eval: false
databraryr::check_duplicate_files_in_folder()
databraryr::check_duplicate_files_in_session()
```

## Logout

```{r}
logout_db()
```

