---
title: "Create/Update/Delete"
format: html
params:
  test_vol_id: 1777
  test_endpoint: "staging"
  prod_api: "https://api.databrary.org"
  staging_api: "https://api.stg-databrary.its.nyu.edu"
---

## About

This documents the results of testing functions that involve file uploads.

::: {.callout-important}
To make use of them, the tester must have write privileges on a Databrary volume.
:::

::: {.callout-warning}
These tests presume that the tester is accessing the test environment using a regular, Authorized Investigator, account.
:::

## Setup

```{r}
#| label: check-endpoint
#| 
assertthat::is.string(params$test_endpoint)
assertthat::is.string(params$prod_api)
assertthat::is.string(params$staging_api)

this_endpoint <- databraryr:::DATABRARY_BASE_URL

if (params$test_endpoint == "production") {
  message("Test target: Production API.")
  if (this_endpoint == params$prod_api) {
    message("Databraryr API target endpoint is correct.")
  } else {
    message(paste0(
      "Target: ",
      params$test_endpoint,
      " | databraryr base: ",
      this_endpoint
    ))
    stop(
      "`databraryr` API target endpoint does not match testing target endpoint. Check ~/.Renviron."
    )
  }
} else if (params$test_endpoint == "staging") {
  message("Test target: Staging API.")
  if (this_endpoint == params$staging_api) {
    message("Databraryr API target endpoint is correct.")
  } else {
    message(paste0(
      "Target: ",
      params$test_endpoint,
      " | databraryr base: ",
      this_endpoint
    ))
    stop(
      "`databraryr` API target endpoint does not match testing target endpoint. Check ~/.Renviron."
    )
  }
} else {
  stop("API endpoint not specified properly")
}
```

```{r}
#| label: "login to Databrary"
library(databraryr)

login_db(email = Sys.getenv("DATABRARY_LOGIN"),
         password = Sys.getenv("DATABRARY_PASSWORD"),
         client_id = Sys.getenv("DATABRARY_CLIENT_ID"),
         client_secret = Sys.getenv("DATABRARY_CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE,
         vb = TRUE)
```

## `create_*` functions

```{r}
#| label: create-folder
x <- assertthat::is.number(params$test_vol_id)
x <- assertthat::assert_that(params$test_vol_id > 0)

folder_name <- date() |> stringr::str_replace_all(pattern = " ", "-")
new_folder <- create_folder(vol_id = params$test_vol_id, name = folder_name)

new_folder
```

```{r}
#| label: create-session
session_name <- date() |> stringr::str_replace_all(pattern = " ", "-")
new_session <- create_session(vol_id = params$test_vol_id, name = session_name)

new_session
```

```{r}
#| label: create-volume-record

record_P001 <- create_volume_record(
  vol_id = params$test_vol_id,
  category_id = 1,
  name = "P001",
  participant = list(birthday = list(
    year = 1776, month = 7, day = 04))
)

record_control_group <- create_volume_record(vol_id = params$test_vol_id,
                                             category_id = 6,
                                             name = "Control group")

record_task_A <- create_volume_record(
  vol_id = params$test_vol_id,
  category_id = 6,
  name = "Task A",
  measures = list("30" = "Extra value")
)

record_P001
record_control_group
record_task_A
```

::: {.callout-note}
2026-05-22: Gilmore needs more guidance about the standard procedure for associating records with sessions and files.
:::

## `upload_file`

```{r}
#| label: upload-png-file

png_path <- "files/upload_01/png_sample.png"

info_png <- upload_file(
  path =  png_path,
  destination_type = "session",
  object_id = new_session$id
)

info_png
```

```{r}
get_upload_status(info_png$status_url)
```

### `bulk_upload`

```{r}
#| label: bulk-upload-to-session-folder
# Upload to session
upload_01_files <- list.files("files/upload_01", full.names = TRUE)
upload_02_files <- list.files("files/upload_02", full.names = TRUE)

# Start the clock!
start_upload <- proc.time()
result_session <- bulk_upload_files(vol_id = params$test_vol_id, session_id = new_session$id,
                  file_paths = upload_01_files, preflight = TRUE)
proc.time() - start_upload

result_session
```

```{r}
#| label: bulk-upload-to-folder
# Upload to folder
start_upload <- proc.time()
result_folder <- bulk_upload_files(vol_id = params$test_vol_id, session_id = NULL,
                  file_paths = c(upload_01_files, upload_02_files),
                  folder_id = new_folder$id, preflight = TRUE)
proc.time() - start_upload

result_folder
```

## `delete_*` functions

```{r}
#| label: delete-functions
#| eval: false
databraryr::delete_record_measure(vol_id = params$test_vol_id, record_id = record_control_group$record_id)

databraryr::delete_session_file()
databraryr::delete_session()

databraryr::delete_folder()

databraryr::delete_volume_record()
```

## `bulk_assign*` functions

```{r}
#| label: bulk-assign
#| eval: false
bulk_assign_records()
bulk_unassign_records()
```

### `bulk_{create,rename,delete}_*`

```{r}
#| label: bulk-create-name-delete
#| eval: false
bulk_create_folders()

bulk_create_records()

bulk_create_records()

bulk_rename_files()

bulk_rename_folders()

bulk_rename_sessions()

bulk_delete_files()

bulk_delete_folders()

bulk_delete_records()

bulk_delete_sessions()
```

### `check_duplicate_*` functions

```{r}
#| label: check-duplicates
#| eval: false
databraryr::check_duplicate_files_in_folder()
databraryr::check_duplicate_files_in_session()
```

## Logout

```{r}
logout_db()
```

