---
title: "Create/Update/Delete"
format: html
params:
  test_vol_id: 1777
  test_endpoint: "production"
  prod_api: "https://api.databrary.org"
  staging_api: "https://api.stg-databrary.its.nyu.edu"
---

## About

This documents the results of testing functions that involve session and folder creation, file uploads, record creation and deletion, and session, folder, and file deletions.

::: callout-important
To make use of them, the tester must have write privileges on a Databrary volume.
:::

::: callout-warning
These tests presume that the tester is accessing the test environment using a regular, Authorized Investigator, account.
:::

## Setup

```{r}
#| label: check-endpoint
#| 
assertthat::is.string(params$test_endpoint)
assertthat::is.string(params$prod_api)
assertthat::is.string(params$staging_api)

this_endpoint <- databraryr:::DATABRARY_BASE_URL

if (params$test_endpoint == "production") {
  message("Test target: Production API.")
  if (this_endpoint == params$prod_api) {
    message("Databraryr API target endpoint is correct.")
  } else {
    message(paste0(
      "Target: ",
      params$test_endpoint,
      " | databraryr base: ",
      this_endpoint
    ))
    stop(
      "`databraryr` API target endpoint does not match testing target endpoint. Check ~/.Renviron."
    )
  }
} else if (params$test_endpoint == "staging") {
  message("Test target: Staging API.")
  if (this_endpoint == params$staging_api) {
    message("Databraryr API target endpoint is correct.")
  } else {
    message(paste0(
      "Target: ",
      params$test_endpoint,
      " | databraryr base: ",
      this_endpoint
    ))
    stop(
      "`databraryr` API target endpoint does not match testing target endpoint. Check ~/.Renviron."
    )
  }
} else {
  stop("API endpoint not specified properly")
}
```

```{r}
#| label: "login to Databrary"
library(databraryr)

login_db(email = Sys.getenv("DATABRARY_LOGIN"),
         password = Sys.getenv("DATABRARY_PASSWORD"),
         client_id = Sys.getenv("DATABRARY_CLIENT_ID"),
         client_secret = Sys.getenv("DATABRARY_CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE,
         vb = TRUE)
```

## Single session/file/folder functions

### `create_{folder,session}*` functions

```{r}
#| label: create-folder
x <- assertthat::is.number(params$test_vol_id)
x <- assertthat::assert_that(params$test_vol_id > 0)

folder_name <- date() |> stringr::str_replace_all(pattern = " ", "-")
new_folder <- create_folder(vol_id = params$test_vol_id, name = folder_name)

new_folder
```

```{r}
#| label: create-session
session_name <- date() |> stringr::str_replace_all(pattern = " ", "-")
new_session <- create_session(vol_id = params$test_vol_id, name = session_name)

new_session
```

### `upload_file`

```{r}
#| label: upload-png-file

png_path <- "files/upload_01/png_sample.png"

info_png <- upload_file(
  path =  png_path,
  destination_type = "session",
  object_id = new_session$id
)

info_png
```

Immediate status report.

```{r}
get_upload_status(info_png$status_url)
```

Sleep for 5 seconds and try again.

```{r}
#| label: wait-5s-check-again
Sys.sleep(5)
get_upload_status(info_png$status_url)
```

### `delete_{folder,file,session}` functions

```{r}
#| label: delete-folder
vol_folders <- list_volume_folders(vol_id = params$test_vol_id) |>
  dplyr::arrange(desc(folder_id))

delete_folder_id <- vol_folders$folder_id[1]

delete_folder(vol_id = params$test_vol_id, folder_id = delete_folder_id)
```

```{r}
#| label: delete-session-file
vol_sessions <- list_volume_sessions(vol_id = params$test_vol_id) |>
  dplyr::arrange(desc(session_id))

delete_session_id <- vol_sessions$session_id[1]

session_files <- list_session_assets(session_id = delete_session_id, vol_id = params$test_vol_id)

session_files

if (dim(session_files)[1] > 0) {
  delete_asset_id <- vol_sessions$session_id[1]
  
  delete_session_file(
    vol_id = params$test_vol_id,
    session_id = delete_session_id,
    file_id = delete_asset_id
  )
  
  list_session_assets(session_id = delete_session_id, vol_id = params$test_vol_id)
} else {
  stop("No files to delete in volume ",
       params$test_vol_id,
       ", session ",
       delete_session_id)
}
```

::: callout-note
2026-05-22: ROG notes that the file metadata does not show that the file has been deleted.
:::

```{r}
#| label: delete-session
vol_sessions <- list_volume_sessions(vol_id = params$test_vol_id) |>
  dplyr::arrange(desc(session_id))

# Before deletion
head(vol_sessions)

delete_session_id <- vol_sessions$session_id[1]

delete_session(vol_id = params$test_vol_id, session_id = delete_session_id)

# After deletion
list_volume_sessions(vol_id = params$test_vol_id) |>
  dplyr::arrange(desc(session_id)) |>
  head()
```

## Bulk functions

We just deleted a test session so we need to create session(s) to upload to first.

### `bulk_create_sessions`

```{r}
#| label: bulk-create-sessions

sessions_created <- bulk_create_sessions(vol_id = params$test_vol_id,
                    session_names = c("bulk-session-01", "bulk-session-02"),
                    source_date = c("1976-07-04", "2026-05-15"))
sessions_created

sessions_created_ids <- c(sessions_created$result[[1]]$id, sessions_created$result[[2]]$id)
```

### `bulk_upload_files` to session

```{r}
#| label: bulk-upload-to-session-folder
#| 
# Upload to session
upload_01_files <- list.files("files/upload_01", full.names = TRUE)
upload_02_files <- list.files("files/upload_02", full.names = TRUE)

# Start the clock!
start_upload <- proc.time()
result_session <- bulk_upload_files(vol_id = params$test_vol_id, session_id = sessions_created_ids[1],
                  file_paths = upload_01_files, preflight = TRUE)
t <- proc.time() - start_upload

timing_df <- tibble::tibble(datetime = Sys.time(), user_t = t[1],
                            system_t = t[2],
                            elapsed_t = t[3],
                            operation = "bulk_upload_files_to_session"
                            )

result_session
```

::: callout-note
2026-05-26: ROG notes that bulk upload takes > 50 s.
:::

### `bulk_create_folders`

```{r}
#| label: bulk-create-folders

folders_created <- bulk_create_folders(vol_id = params$test_vol_id,
                    folder_names = c("bulk-folder-01", "bulk-folder-02"),
                    source_date = c("1976-07-04", "2026-05-15"))
folders_created

folders_created_ids <- c(folders_created$result[[1]]$id, folders_created$result[[2]]$id)
```

### `bulk_upload_files` to folder

Let's upload to a folder with files from two subfolders.

```{r}
#| label: bulk-upload-to-folder

start_upload <- proc.time()
result_folder <- bulk_upload_files(vol_id = params$test_vol_id, session_id = NULL,
                  file_paths = c(upload_01_files, upload_02_files),
                  folder_id = folders_created_ids[1], preflight = TRUE)

t <- proc.time() - start_upload

timing_df <- timing_df |>
  tibble::add_row(datetime = Sys.time(), user_t = t[1],
                            system_t = t[2],
                            elapsed_t = t[3],
                            operation = "bulk_upload_files_to_folder"
                            )
result_folder
```

### `bulk_rename_{files,sessions,folders}` functions

In the code below, I set `n_to_rename` to 3, but confirm that there are at least 3 files or sessions before renaming. If there aren't enough files or sessions, the chunk exits with an error message.

```{r}
#| label: bulk-rename-files
n_to_rename <- 3

these_files <- list_session_assets(session_id = sessions_created_ids[1], 
                                   vol_id = params$test_vol_id)

if(dim(these_files)[1] < n_to_rename) {
  n_to_rename = dim(these_files)[1]
}

if (n_to_rename < 1) {
  stop("No files to rename in volume ", params$test_vol_id, 
       ", session ", new_session$id)
}

file_asset_ids <- these_files$asset_id[1:n_to_rename]
new_file_names <- stringr::str_replace(these_files$asset_name[1:n_to_rename], 
                                       pattern = "_", replacement = "--")

bulk_rename_these <- bulk_rename_files(vol_id = params$test_vol_id,
                  session_id = sessions_created_ids[1],
                  file_ids = file_asset_ids,
                  new_names = new_file_names)

renamed_files <- list_session_assets(session_id = sessions_created_ids[1], 
                                     vol_id = params$test_vol_id)

cbind(old_names = these_files$asset_name[1:n_to_rename], 
      new_names = renamed_files$asset_name[1:n_to_rename])
```

::: {.callout-warning}
Bulk renaming requires a fix to the duplicate id and name bug.
:::

```{r}
#| label: bulk-rename-sessions

n_to_rename <- 3

these_sessions <- list_volume_sessions(vol_id = params$test_vol_id) |> 
  dplyr::arrange(desc(session_id)) |>
  dplyr::distinct()

if (dim(these_sessions)[1] < 1) {
  stop("No sessions to rename in volume ", params$test_vol_id)
}

session_ids_unique <- these_sessions$session_id |> 
  unique()

if(length(session_ids_unique) < n_to_rename) {
  n_to_rename = length(session_ids_unique)
}

selected_session_ids <- session_ids_unique[1:n_to_rename]

# these_sessions <- these_sessions |>
#   dplyr::filter(session_id %in% selected_session_ids)

sessions_to_rename <- these_sessions |>
  dplyr::filter(session_id %in% selected_session_ids)

unique_session_ids <- unique(sessions_to_rename$session_id)
new_session_names <- paste0("new_session_", 1:length(unique_session_ids))

bulk_rename_these <- bulk_rename_sessions(vol_id = params$test_vol_id, 
                                          session_ids = unique_session_ids,
                                          new_names = new_session_names)

renamed_sessions <- list_volume_sessions(vol_id = params$test_vol_id) |> 
  dplyr::arrange(desc(session_id)) |>
  dplyr::distinct()

cbind(old_names = these_sessions$session_name, 
      new_names = renamed_sessions$session_name)
```

```{r}
#| label: bulk-rename-folders

n_to_rename <- 3

these_folders <- list_volume_folders(vol_id = params$test_vol_id) |> 
  dplyr::arrange(desc(folder_id)) |>
  dplyr::distinct()

if (dim(these_folders)[1] < 1) {
  stop("No sessions to rename in volume ", params$test_vol_id)
}

folder_ids_unique <- these_folders$folder_id |> 
  unique()

if(length(folder_ids_unique) < n_to_rename) {
  n_to_rename = length(folder_ids_unique)
}

selected_folder_ids <- folder_ids_unique[1:n_to_rename]

# these_folders <- these_folders |>
#   dplyr::filter(folder_id %in% selected_folder_ids)

folders_to_rename <- these_folders |>
  dplyr::filter(folder_id %in% selected_folder_ids)

unique_folder_ids <- unique(folders_to_rename$folder_id)
new_folder_names <- paste0("new_folder_", 1:length(unique_folder_ids))

bulk_rename_these <- bulk_rename_folders(vol_id = params$test_vol_id, 
                                          folder_ids = unique_folder_ids,
                                          new_names = new_folder_names)

renamed_folders <- list_volume_folders(vol_id = params$test_vol_id) |> 
  dplyr::arrange(desc(folder_id)) |>
  dplyr::distinct()

cbind(old_names = these_folders$folder_name, 
      new_names = renamed_folders$folder_name)
```

### `check_duplicate_files_in_{folder,session}`

```{r}
#| label: check-duplicates
#| eval: false
check_duplicate_files_in_folder(vol_id = params$test_vol_id, filenames = "new_")
check_duplicate_files_in_session(vol_id = params$test_vol_id, filenames = "new_")
```

### `bulk_delete_{sessions,folders}`

```{r}
#| label: bulk-delete-sessions

bulk_delete_sessions(vol_id = params$test_vol_id,
                     session_ids <- sessions_created_ids)
```

```{r}
#| label: bulk-delete-folders

bulk_delete_folders(vol_id = params$test_vol_id,
                     session_ids <- folders_created_ids)
```

## Save timing file

```{r}
timing_fn <- paste0("timing-data-", format(Sys.time(), "%Y-%m-%d-%H%M%S"), ".csv")
readr::write_csv(timing_df, file.path("csv", timing_fn))
```

## Logout

```{r}
logout_db()
```
